---
title: "snakecase"
output: rmarkdown::github_document
---

[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/Tazinho/snakecase?branch=master&svg=true)](https://ci.appveyor.com/project/Tazinho/snakecase) [![Travis-CI Build Status](https://travis-ci.org/Tazinho/snakecase.svg?branch=master)](https://travis-ci.org/Tazinho/snakecase) [![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/snakecase)](https://cran.r-project.org/package=snakecase) [![Coverage Status](https://img.shields.io/codecov/c/github/Tazinho/snakecase/master.svg)](https://codecov.io/github/Tazinho/snakecase?branch=master)

<!--A small package with functions to convert column names of data.frames (or strings
in general) to different cases like snake_case, smallCamel- and BigCamelCase among others. Also high level features for more advanced case conversions are provided via `to_any_case()`.-->
The snakecase package contains five specific caseconverter functions and one more general highlevel function with additional functionality.

## Install

```{r, results='hide', message=FALSE}
# install.packages("devtools")
# devtools::install_github("Tazinho/snakecase", ref = "devversion-01", force = TRUE)
devtools::install_github("Tazinho/snakecase")
```

# Usage 

## Specific caseconverters

```{r, collapse=TRUE}
# devtools::install_github("Tazinho/snakecase")
library(snakecase)
strings <- c("this Is a Strange_string", "AND THIS ANOTHER_One")

to_snake_case(strings)

to_small_camel_case(strings)

to_big_camel_case(strings)

to_screaming_snake_case(strings)

to_parsed_case(strings)
```

## Highlevel caseconverter

The funtion `to_any_case()` can do everything that the others can and also adds some extra highlevel functionaliy.

### Default usage

```{r, collapse=TRUE}
to_any_case(strings, case = "snake")

to_any_case(strings, case = "small_camel")

to_any_case(strings, case = "big_camel")

to_any_case(strings, case = "screaming_snake")

to_any_case(strings, case = "parsed")
```

### Pre -and postprocessing

By default only whitespaces, underscores and some patterns of mixed lower/upper case letter combinations are recognized as word boundaries. You can specify anything as a word boundary which is a valid stringr regular expression:

```{r, collapse=TRUE}
strings2 <- c("this - Is_-: a Strange_string", "ÄND THIS ANOTHER_One")

to_snake_case(strings2)

to_any_case(strings2, case = "snake", preprocess = "-|\\:")
```

You can also specify a different separator than `"_"` or `""` via `postprocess`:

```{r, collapse = TRUE}
to_any_case(strings2, case = "snake", preprocess = "-|\\:", postprocess = " ")

to_any_case(strings2, case = "big_camel", preprocess = "-|\\:", postprocess = "//")
```

### Pre -and postfix

You can set pre -and suffixes:

```{r, collapse=TRUE}
to_any_case(strings2, case = "big_camel", preprocess = "-|\\:", postprocess = "//",
            prefix = "USER://", postfix = ".exe")
```

### Special characters

If you have problems with special characters on your plattform, you can replace them via `replace_special_characters = TRUE`:

```{r, collapse = TRUE, eval = FALSE}
strings3 <- c("ßüss üß ä stränge sträng", "unrealistisch aber nützich")

to_any_case(strings3, case = "screaming_snake", replace_special_characters = TRUE)
## [1] "SSUESS_UESS_AE_STRAENGE_STRAENG" "UNREALISTISCH_ABER_NUETZICH"
```
<!--
```{r, collapse=TRUE, message=FALSE}
library(snakecase)

strings <- c("smallCamelCase", "BigCamelCase", "SCREAMING_SNAKE_CASE",
             "RRRProjectRRProject", "große Männer_1.2_3-4/5", NA)

# conversion
to_snake_case(strings)

to_small_camel_case(strings)

to_big_camel_case(strings)

to_screaming_snake_case(strings)

to_any_case(strings,
            case = "big_camel", 
            preprocess = "\\.|-|/", 
            replace_special_characters = TRUE)

to_any_case(strings,
            case = "screaming_snake",
            preprocess = "\\.|-|/",
            postprocess = "/",
            prefix = "USER/",
            postfix = ".exe",
            replace_special_characters = TRUE)

# test if your names are a valid case (consistent with this package)
# for example smallCamelCase
strings == to_small_camel_case(strings)

# compare input and output
library(dplyr)

tibble(inp = strings, outp = to_small_camel_case(strings)) %>% 
  mutate(compare = inp == outp)
```
-->

# Design Philosophy

## Practical influences

Conversion to a specific target case is not always obvious or unique. In general a clean conversion
can only be guaranted, when the input-string is meaningful.

Take for example a situation where you have IDs for some customers. Instead of calling the column "CustomerID" you abbreviate it to "CID". Without further knowledge about the meaning of CID it will be impossible to know that it should be converted to "c_id", when using `to_snake_case()`. Instead it will be converted to:

```{r, collapse=TRUE}
to_snake_case("CID")
```

We could have also converted to "c_i_d" and if we don't know the meaning of "CID", we can't decide which one is the better solution. However it is easy to exclude specific approaches by counterexamples. So in practice it might be nicer to convert "SCREAMING_SNAKE_CASE" to "screaming_snake_case" instead of "s_c_r_e_a_m_i_n_g_s_n_a_k_e_c_a_s_e" (or "screamin_g_snak_e_cas_e" or "s_creaming_s_nake_c_ase"), which means that also "cid" is preferable to "c_i_d" (or "c_id" or "ci_d") without further knowledge.

Since the computer can't know, that we want "c_id" by himself. It is easiest, if we provide him with the right information (here in form of a valid PascalCase syntax):

```{r, collapse=TRUE}
to_snake_case("CId")
```

In this way it is guaranteed to get the correct conversion and the only chance of an error lies in an accidentally wrong provided input string or a bug in the converter function `to_snake_case()`.

## Consistent behaviour

In many scenarios the analyst doesn't have a big influence on naming conventions and sometimes there might occur situations where it is not possible to find out the exact meaning of a variable name, even if we ask the original author. In some cases data might also have been named by a machine and the results can be relatively technically. So in general it is a good idea to compare the input of the case converter functions with their output, to see if the intended meanings at least seem to be preserved.

To make this as painless as possible, it is best to provide a logic that is robust and can handle also relatively complex cases. Note for example the string "RStudio". How should one convert it to snake case? We have seen a similar example with "CId", but for now we focus on sth. different. In case of "RStudio", we could convert to: 

1. "r_s_tudio",
1. "rs_tudio" or
1. "r_studio".

If we are conservative about any assumptions on the meaning of "RStudio", we can't decide which is the correct conversion. It is also not valid to assume that "RStudio" was intentionally written in PascalCase. Of course we know that "r_studio" is the correct solution, but we can get there also via different considerations. Let us try to convert our three possible translations (back) to PascalCase and from there back to snake case. What should the ouput look like?

1. r_s_tudio -> RSTudio -> r_s_t_udio
1. rs_tudio  -> RsTudio -> rs_tudio
1. r_studio  -> RStudio -> r_studio

Both of the first two alternatives can't be consistently converted back to a valid Pascal case input ("RStudio") and with the first logic the further snake case conversion seems to be complete nonsense. Only the latter case is consistent, when converting back to PascalCase, which is the case of the input "RStudio". It is also consistent to itself, when converting from PascalCase back to snake_case.  

In this way, we can get a good starting point on how to convert specifc strings to valid snake_case. Once we have a clean snake_case conversion, we can easily convert further to smallCamelCase, BigCamelCase, SCREAMING_SNAKE_CASE or anything else.

## Three rules of consistency

In the last sections we have seen, that it is reasonable to bring a specific conversion from an input string to some standardized case into question. We have also seen, that it is helpful to introduce some tests on the behaviour of a specific conversion pattern in related cases. The latter can help to detect inappropriate conversions and also establishes a consistent behaviour when converting exotic cases or switching between standardized cases. Maybe we can generalize some of these tests and introduce some kind of consisteny patterns. This would enable us that whenever inappropriate or non-unique possibilities for conversions appear, we have rules that help us to deal with this situation and help to exclude some inconsistent conversion alternatives.

During the development of this package I recognized three specific rules that seem reasonable to be valid whenever cases are converted. To be more general we just use `to_x()` and `to_y()` to refer to any two differing converter functions from this package.

1. When we have converted to a standardized case, a new conversion to the case should not change the output:

    `to_x(to_x(string)) = to_x(string)`  

1. When converting to a specific case, it should not matter if a conversion to another case happened already:

    `to_y(to_x(string)) = to_y(string)`  

1. It should always be possible to switch between different cases, without any loss of information:  

    `to_x(to_y(to_x(string))) = to_x(string)`  

Note that it can easily be shown, that rule three follows from the first and the second rule. However, it seems reasonable to express each by its own, since they all have an interpretation and together they give a really good intuition about the properties of the converter functions.

# Testing

To give a meaningful conversion for different cases, we systematically designed meaningful testcases for conversion to snake, small- and big camel case among others.
To be consistent regarding the conversion between different cases, we also test the rules above on all example input strings, which are shown below.
<!--Note that equality in this equation is only one criterion and it still doesn't
imply a unique solution on how to translate an initial string argument to snake or camel case. (Note that also `to_xxx(string) = to_xxx(string)` seems desirable). However, for the 
following testcases, also these two equations are tested.-->


```{r, echo = FALSE}
cases <- c(NA, "snake_case", "snakeCase",
           "SnakeCase", "_", "snake_Case",
           "_", "SNake", "Snake",
           "s_nake", "sn_ake",  "_",
           "SNaKE", "SNaKEr", "s_na_k_er",
           "_", "SNAKE SNAKE CASE", "_",
           "snakeSnakECase", "SNAKE snakE_case", "_",
           "ssRRss", "ssRRRR")            

# cases <- c(NA,
#            "snake_case", "snakeCase",
#            "SnakeCase", "_", "snake_Case", 
#            "_", "SNake", "Snake",
#            "s_nake", "sn_ake", "_",
#            "SNaKE", "SNaKEr", "s_na_k_er", "_",
#            "SNAKE SNAKE CASE", "_",
#            "snakeSnakECase", "SNAKE snakE_case", "_",
#            "bangBooMBang",
#            "upPER", "CId", "_",
#            "___", ".", "...",
#            "Sepal.Width", "Var 1", "Var-2",
#            "Var.3", "Var4",
#            "SnakeCase",
#            "Snake-Case",
#            "Snake Case",
#            "Snake  -  Case")
# 
# `As intended?` = c("yes", "yes", "yes",
#                                                "yes", "", "yes",
#                                                "", "yes", "yes",
#                                                "yes", "yes", "",
#                                                "yes", "yes", "yes",
#                                                "", "yes", "yes",
#                                                "yes", "", "yes",
#                                                "_ ?", "",
#                                                "_ X",
#                                                "_ X", "_ ? (maybe c_id)", "_ ?",
#                                                "_ ?", "_ ?", "_ ?",
#                                                "_ X", "_ ? (maybe var1)", "_ ?", 
#                                                "_ ? (maybe var3)", "_ X",
#                                                "","")

knitr::kable(tibble::tibble(nr = seq_along(cases),
                            examples = cases,
                            snake_case = snakecase::to_snake_case(cases),
                            #snake_case_dev = snakecase::to_snake_case_dev(cases),
                            smallCamelCase = snakecase::to_small_camel_case(cases),
                            BigCamelCase = snakecase::to_big_camel_case(cases)
                            )
             )
```

# Related Resources

* [The state of naming conventions in R, Bååth 2012, R Journal](https://lup.lub.lu.se/search/publication/e324f252-1d1c-4416-ad1f-284d4ba84bf9) [Download article](journal.r-project.org/archive/2012-2/RJournal_2012-2_Baaaath.pdf)
* [Consistent naming conventions in R, Lovelace 2014, RBloggers](https://www.r-bloggers.com/consistent-naming-conventions-in-r/)
* [What is your preferred style for naming variables in R?, Stackoverflowquestion 2009](http://stackoverflow.com/questions/1944910/what-is-your-preferred-style-for-naming-variables-in-r)
* [Are there any official naming conventions in R?, stackoverflowquestion 2012](http://stackoverflow.com/questions/10013545/are-there-any-official-naming-conventions-for-r)
* [`clean_names()` function()](https://github.com/sfirke/janitor/blob/master/R/clean_names.R) from the [janitor package](https://github.com/sfirke/janitor)
* [`to_camel` function()](https://github.com/Rapporter/rapportools/blob/master/R/utils.R) from the [rapporttools package](https://github.com/Rapporter/rapportools)