---
title: "snakecase"
output: rmarkdown::github_document
---

[![Travis-CI Build Status](https://travis-ci.org/Tazinho/snakecase.svg?branch=master)](https://travis-ci.org/Tazinho/snakecase)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/Tazinho/snakecase?branch=master&svg=true)](https://ci.appveyor.com/project/Tazinho/snakecase)

A small package with functions to convert column names of data.frames (or strings
in general) to snake_case, smallCamel- and BigCamelCase.

## Install

```{r, results='hide', message=FALSE}
# install.packages("devtools")
devtools::install_github("Tazinho/snakecase", ref = "devversion-01")
```

## Usage

```{r, collapse=TRUE}
library(snakecase)

strings <- c("smallCamelCase", "BigCamelCase", "mixed_Case", "BIGGY BIGGY BIGGY", NA)

to_snake_case(strings)

to_small_camel_case(strings)

to_big_camel_case(strings)
```

## Current behaviour (this part is work in progress)

Conversion to camel case is not always obvious. Below you can see the current bahaviour. Those examples that behave as intended (X) and are also tested (`*Td*`) will be stable in the future.
Others might be considered to be changed.

In general it might be desirable to have at least sth. like "pairwise inversity" of the three `to_xxx` functions on the space of `to_xxx(string)`. So it might be a good criterion if the following equation holds for any input string:

1. `to_A(to_B(to_A(string))) = to_A(string)`, (note that this might be equivalent to `to_A(to_B(string))) = to_A(string)`)

where `to_A` and to `to_B` can be `to_snake_case`, `to_small_camel_case` and `to_big_camel_case`.

Note that equality in this equation is only one criterion and it still doesn't
imply a unique solution on how to translate an initial string argument to snake or camel case. (Note that also `to_xxx(string) = to_xxx(string)` seems desirable). However, for the 
following testcases, also these two equations are tested.

```{r, echo = FALSE}
cases <- c(NA,
           "snake_case", "snakeCase",
           "SnakeCase", "_", "snake_Case", 
           "_", "SNake", "Snake",
           "s_nake", "sn_ake", "_",
           "SNaKE", "SNaKEr", "s_na_k_er", "_",
           "SNAKE SNAKE CASE", "_",
           "snakeSnakECase", "SNAKE snakE_case", "_",
           "bangBooMBang",
           "upPER", "CId", "_",
           "___", ".", "...",
           "Sepal.Width", "Var 1", "Var-2",
           "Var.3", "Var4",
           "SnakeCase",
           "Snake-Case",
           "Snake Case",
           "Snake  -  Case")

knitr::kable(tibble::tibble(nr = seq_along(cases),
                            examples = cases,
                            snake_case = snakecase::to_snake_case(cases),
                            #snake_case_dev = snakecase::to_snake_case_dev(cases),
                            smallCamelCase = snakecase::to_small_camel_case(cases),
                            BigCamelCase = snakecase::to_big_camel_case(cases),
                            `As intended?` = c("\\*Td\\*, X", "\\*Td\\*, X", "\\*Td\\*, X",
                                               "\\*Td\\*, X", "", "\\*Td\\*, X",
                                               "", "\\*Td\\*, ?", "\\*Td\\*, X",
                                               "\\*Td\\*, X", "\\*Td\\*, X",
                                               "", "\\*Td\\*, ?", "\\*Td\\*, ?",
                                               "\\*Td\\*, X",
                                               "", "X \\*Td\\*",
                                               "",
                                               ", \\*Td\\*",
                                               "_ ?", "",
                                               "_ X",
                                               "_ X", "_ ? (maybe c_id)", "_ ?",
                                               "_ ?", "_ ?", "_ ?",
                                               "_ X", "_ ? (maybe var1)", "_ ?", 
                                               "_ ? (maybe var3)", "_ X",
                                               "","","",""))
             )
```