---
title: "Caseconverters"
author: "Malte Grosser"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Caseconverters}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

The snakecase package contains five specific caseconverter functions and one more general highlevel function with added functionality.

## Specific caseconverters

```{r, collapse=TRUE}
# devtools::install_github("Tazinho/snakecase")
library(snakecase)
strings <- c("this Is a Strange_string", "AND THIS ANOTHER_One")

to_snake_case(strings)

to_small_camel_case(strings)

to_big_camel_case(strings)

to_screaming_snake_case(strings)

to_parsed_case(strings)
```

## Highlevel casesconverter

The funtion `to_any_case()` can do everything that the others can and also adds some extra highlevel functionaliy.

### Default usage

```{r, collapse=TRUE}
to_any_case(strings, case = "snake")

to_any_case(strings, case = "small_camel")

to_any_case(strings, case = "big_camel")

to_any_case(strings, case = "screaming_snake")

to_any_case(strings, case = "parsed")
```

### Pre -and postprocessing

By default only whitespaces, underscores and some patterns of mixed lower/upper case letter combinations are recognized as word boundaries. You can specify anything as a word boundary which is a valid stringr regular expression:

```{r, collapse=TRUE}
strings2 <- c("this - Is_-: a Strange_string", "ÄND THIS ANOTHER_One")

to_snake_case(strings2)

to_any_case(strings2, case = "snake", preprocess = "-|\\:")
```

You can also specify a different separator than `"_"` or `""` via `postprocess`:

```{r, collapse = TRUE}
to_any_case(strings2, case = "snake", preprocess = "-|\\:", postprocess = " ")

to_any_case(strings2, case = "big_camel", preprocess = "-|\\:", postprocess = "//")
```

### Pre -and postfix

You can set pre -and suffixes:

```{r, collapse=TRUE}
to_any_case(strings2, case = "big_camel", preprocess = "-|\\:", postprocess = "//",
            prefix = "USER://", postfix = ".exe")
```

### Special characters

If you have problems with special characters on your plattform, you can replace them via `replace_special_characters = TRUE`:

```{r, collapse = TRUE, eval = FALSE}
strings3 <- c("ßüss üß ä stränge sträng", "unrealistisch aber nützich")

to_any_case(strings3, case = "screaming_snake", replace_special_characters = TRUE)
## [1] "SSUESS_UESS_AE_STRAENGE_STRAENG" "UNREALISTISCH_ABER_NUETZICH"
```

### Vectorisation

`to_any_case()` is vectorised over `preprocess`, `postprocess`, `prefix` and `postfix`.

## Further reading

If you are interested in the design of this package, you can find more information on its [github page](https://github.com/Tazinho/snakecase).