---
title: "Case converters"
author: "Malte Grosser"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Caseconverters}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Basic examples

Default case is snake case

```{r, collapse = TRUE}
library(snakecase)
to_any_case("veryComplicatedString")
```

Dots and other special characters may have a special intention

```{r, collapse = TRUE}
to_any_case("malte.grosser@gmail.com")
```

When it is clear that they are separators, you can supply them as a regex to the `sep_in` argument

```{r, collapse = TRUE}
to_any_case(names(iris), sep_in = "\\.")
```

This is especially handy, when special characters have a meaning as a separator or for example as a decimal mark

```{r, collapse = TRUE}
to_any_case("Pi.Value:3.14", sep_in = ":|(?<!\\d)\\.")
```

Of course other cases are supported (`case`) and separators can be adjusted (`postprocess`)

```{r, collapse = TRUE}
to_any_case(names(iris), sep_in = "\\.", case = "upper_camel", postprocess = " ")
```

And you might want to remove special characters along the way

```{r, collapse = TRUE}
to_any_case("Doppelgänger is originally german", 
            replace_special_characters = "german", case = "upper_camel")
```

All of the cases like: snake, lower_camel, upper_camel, all_caps, lower_upper, upper_lower and mixed are based on parsed case

```{r, collapse = TRUE}
to_any_case("THISIsHOW IAmPARSED!", case = "parsed")
```

Shortcut wrappers like `to_snake_case`, `to_lower_camel_case` etc. are available.

Be aware that automatic case conversion depends on the input string and it is recommended to verify the results. So you might want to pipe these into `dput()` (and hardcode name changes instead of blindly trusting `to_any_case()`'s output)

```{r, collapse = TRUE}
dput(to_any_case(c("SomeBAdInput", "someGoodInput")))
```

If you are interested in the design of this package, you can find more information on its [github page](https://github.com/Tazinho/snakecase).